---
title: "Config view"
subtitle: "The same facts, in the compact `amr.assessment_config.v1` authoring shape"
toc: true
---

```{r}
#| include: false
source("_common.R")
```

The registry stores metadata as **normalized annual sidecars** — one file per
`jurisdiction × system × year` (browse them in the [Catalog](index.qmd)). That
shape is optimized for versioning and querying, not for reading a whole program
at a glance.

This page shows the **same facts** projected into the compact *assessment config*
shape (`amr.assessment_config.v1`) — the DRY authoring lens contributed by a
colleague and adopted as a projection in [ADR-010]. It is a **view over canonical
v2**, generated by `amrr::as_config()`, not a second source of truth: one file per
program, reusable named **level schemes** referenced by tests, a `content_area ×
grade → test` **map**, and unified per-grade **cuts** (`{loss, hoss, values}`).
`amrr::read_config()` expands it back into sidecars, so authoring can happen in
whichever shape is more convenient.

Two things the compact shape must carry that a bare grade list cannot:

- **`intended_enrollment_grade`** (`fixed` / `variable`) — ILEARN tests grades
  3–8 yet is `fixed` (each grade has its own form); the enrollment axis is a
  distinct fact from the grade list (ADR-009).
- The **`eoc`** cut key for end-of-course tests — one instrument-level standard
  rather than a per-grade cut (ADR-010).

Extension blocks (`measurement.*`), provenance, comparability, and source
documents are intentionally dropped by the projection; consult the full record
for those.

```{r}
#| output: asis
cfgs <- amr_configs()
if (!length(cfgs)) {
  cat("_No config projections found — run `make build` to generate `build/config/`._\n")
} else {
  for (cfg in cfgs) amr_render_config(cfg)
}
```

[ADR-010]: https://github.com/CenterForAssessment/assessment-metadata-registry/blob/main/wiki/decisions/010-config-view-reconciliation.md
