---
title: "Assessment Metadata Registry"
pagetitle: "Assessment Metadata Registry"
toc: false
---

```{r}
#| label: setup
#| include: false
source("_common.R")
library(reactable)

recs   <- amr_all_records()
stamp  <- amr_registry_stamp()
n_assess <- sum(vapply(recs, function(r) !amr_is_accountability(r), logical(1)))
n_acct   <- length(recs) - n_assess
jurs     <- unique(vapply(recs, function(r) r$jurisdiction$id, character(1)))
years    <- as.integer(vapply(recs, amr_year, character(1)))

# One catalog row per sidecar.
df <- do.call(rbind, lapply(recs, function(r) {
  sys <- amr_system(r)
  scope <- if (amr_is_accountability(r)) sprintf("%d targets", length(r$targets %||% list()))
           else sprintf("%d content areas", length(r$content_areas %||% list()))
  data.frame(
    Jurisdiction = r$jurisdiction$name %||% r$jurisdiction$id,
    System = sys$name %||% sys$id,
    Type = amr_type(r),
    Year = amr_year(r),
    Scope = scope,
    Vendor = r$administration$vendor %||% "—",
    Status = r$status %||% "",
    Confidence = r$source_confidence %||% "",
    slug = amr_slug(r),
    stringsAsFactors = FALSE
  )
}))
```

::: {.amr-masthead}
[Canonical · version-controlled · derived]{.amr-kicker}

# A catalog of state assessment metadata

::: {.amr-lede}
Version-controlled JSON sidecars are the source of truth for assessment- and
accountability-system metadata — identities, vendors, vertical scales, achievement
levels, cutscores, comparability caveats, and accountability targets. Everything
below is **rendered from those sidecars**; browse a record for a human-readable view
or the raw JSON.
:::

```{r}
#| output: asis
span <- if (length(years)) sprintf("%d–%d", min(years), max(years)) else "—"
cat(sprintf(
'<div class="amr-statline">
  <div class="amr-stat"><span class="amr-stat-n">%d</span><span class="amr-stat-l">records</span></div>
  <div class="amr-stat"><span class="amr-stat-n">%d</span><span class="amr-stat-l">jurisdictions</span></div>
  <div class="amr-stat"><span class="amr-stat-n">%d</span><span class="amr-stat-l">assessment</span></div>
  <div class="amr-stat"><span class="amr-stat-n">%d</span><span class="amr-stat-l">accountability</span></div>
  <div class="amr-stat"><span class="amr-stat-n">%s</span><span class="amr-stat-l">years</span></div>
</div>',
  length(recs), length(jurs), n_assess, n_acct, span))
```
:::

## Catalog {.unnumbered}

Search across every record, or filter a column. Select a **system** to open its record.

```{r}
#| label: catalog
reactable(
  df[, c("Jurisdiction", "System", "Type", "Year", "Scope", "Vendor", "Status", "Confidence")],
  columns = list(
    Jurisdiction = colDef(minWidth = 150),
    System = colDef(minWidth = 160, cell = function(value, index) {
      htmltools::tags$a(class = "amr-rowlink", href = amr_page(df$slug[index]), value)
    }),
    Type = colDef(width = 130),
    Year = colDef(width = 80),
    Scope = colDef(minWidth = 120),
    Status = colDef(width = 110, align = "center", html = TRUE,
                    cell = function(value) amr_badge(value, "status")),
    Confidence = colDef(width = 120, align = "center", html = TRUE,
                        cell = function(value) amr_badge(value, "conf"))
  ),
  searchable = TRUE,
  filterable = TRUE,
  defaultPageSize = 15,
  showPageSizeOptions = TRUE,
  pageSizeOptions = c(15, 30, 60),
  highlight = TRUE,
  borderless = TRUE,
  defaultSorted = list(Jurisdiction = "asc", System = "asc", Year = "desc"),
  class = "amr-catalog"
)
```

```{r}
#| output: asis
if (length(stamp)) {
  cat(sprintf(
    '<p class="amr-callno" style="margin-top:1rem">Built from registry commit <code>%s</code>%s · %s</p>',
    substr(stamp$git_sha %||% "—", 1, 12),
    if (isTRUE(stamp$dirty)) " (dirty)" else "",
    stamp$built_at %||% ""))
}
```
