---
title: "The schema"
subtitle: "The JSON Schema contracts that every sidecar must satisfy"
---

```{r}
#| include: false
source("_common.R")
SCHEMA_DIR <- Sys.getenv("AMRR_SCHEMA_DIR", file.path("..", "schemas"))
read_schema <- function(f) fromJSON(file.path(SCHEMA_DIR, f), simplifyVector = FALSE)

esc <- function(x) htmltools::htmlEscape(x %||% "")

# Render one property as a bordered field; recurse into nested objects / array items.
render_field <- function(name, p, required, depth = 0) {
  p <- p %||% list()
  # Resolve the declared type / shape.
  type <- p$type %||% (
    if (!is.null(p$const)) "const" else
    if (!is.null(p$enum)) "enum" else
    if (!is.null(p[["$ref"]])) "$ref" else
    if (!is.null(p$oneOf) || !is.null(p$anyOf)) "union" else "any")
  if (is.list(type)) type <- paste(unlist(type), collapse = " | ")

  meta <- sprintf("<span>%s</span>", esc(type))
  if (required) meta <- paste0(meta, "<span class='amr-req'>required</span>")
  if (!is.null(p$const)) meta <- paste0(meta, sprintf("<span>= <code>%s</code></span>", esc(p$const)))
  if (!is.null(p$pattern)) meta <- paste0(meta, sprintf("<span><code>%s</code></span>", esc(p$pattern)))

  enum_html <- ""
  if (!is.null(p$enum)) {
    enum_html <- sprintf("<div class='amr-enum'>%s</div>",
      paste(sprintf("<code>%s</code>", vapply(p$enum, function(e) esc(e), character(1))), collapse = " "))
  }
  desc <- if (!is.null(p$description)) sprintf("<p class='amr-field-desc'>%s</p>", esc(p$description)) else ""

  cat(sprintf(
    "<div class='amr-field' style='margin-left:%drem'><span class='amr-field-name'>%s</span><span class='amr-field-meta'>%s</span>%s%s</div>\n",
    depth * 1L, esc(name), meta, desc, enum_html))

  # Recurse: object properties, then array-of-object items.
  if (identical(type, "object") && !is.null(p$properties) && depth < 3) {
    req <- unlist(p$required %||% list())
    for (nm in names(p$properties)) render_field(nm, p$properties[[nm]], nm %in% req, depth + 1)
  }
  items <- p$items
  if (identical(type, "array") && !is.null(items) && !is.null(items$properties) && depth < 3) {
    req <- unlist(items$required %||% list())
    cat(sprintf("<div class='amr-callno' style='margin-left:%drem'>each item:</div>\n", (depth + 1L)))
    for (nm in names(items$properties)) render_field(nm, items$properties[[nm]], nm %in% req, depth + 1)
  }
  # Map values (additionalProperties as a schema).
  ap <- p$additionalProperties
  if (identical(type, "object") && is.list(ap) && !is.null(ap$type) && depth < 3) {
    cat(sprintf("<div class='amr-callno' style='margin-left:%drem'>values (keyed map):</div>\n", (depth + 1L)))
    render_field("&lt;key&gt;", ap, FALSE, depth + 1)
  }
}

render_schema <- function(schema) {
  req <- unlist(schema$required %||% list())
  for (nm in names(schema$properties %||% list())) {
    render_field(nm, schema$properties[[nm]], nm %in% req, 0)
  }
}
```

Each authored sidecar is validated against its JSON Schema before any derivation.
A field marked [required]{.amr-req} must be present; fields with an `enum` accept only the
listed values. These schemas are the executable Tier A contract — this page renders them
directly, so it never drifts from what the validator enforces. **v2** (ADR-009) is
canonical; **v1** remains accepted during the migration window.

::: {.panel-tabset}

## Assessment (v2)

```{r}
#| output: asis
s <- read_schema("amr.assessment.v2.schema.json")
cat("```{=html}\n")
cat(sprintf("<p class='amr-lede'>%s</p>\n", esc(s$description)))
cat(sprintf("<p class='amr-callno'>%s · <code>%s</code></p>\n", esc(s$title), esc(s[["$id"]])))
render_schema(s)
cat("\n```\n")
```

## Accountability (v2)

```{r}
#| output: asis
s <- read_schema("amr.accountability.v2.schema.json")
cat("```{=html}\n")
cat(sprintf("<p class='amr-lede'>%s</p>\n", esc(s$description)))
cat(sprintf("<p class='amr-callno'>%s · <code>%s</code></p>\n", esc(s$title), esc(s[["$id"]])))
render_schema(s)
cat("\n```\n")
```

## Assessment (v1, migration window)

```{r}
#| output: asis
s <- read_schema("amr.assessment_system.v1.schema.json")
cat("```{=html}\n")
cat(sprintf("<p class='amr-lede'>%s</p>\n", esc(s$description)))
cat(sprintf("<p class='amr-callno'>%s · <code>%s</code></p>\n", esc(s$title), esc(s[["$id"]])))
render_schema(s)
cat("\n```\n")
```

## Accountability (v1, migration window)

```{r}
#| output: asis
s <- read_schema("amr.accountability_system.v1.schema.json")
cat("```{=html}\n")
cat(sprintf("<p class='amr-lede'>%s</p>\n", esc(s$description)))
cat(sprintf("<p class='amr-callno'>%s · <code>%s</code></p>\n", esc(s$title), esc(s[["$id"]])))
render_schema(s)
cat("\n```\n")
```

:::
